---
title: "HUDM5124Assignment9"
author: "Zhuqian Zhou"
date: "2017/3/27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 1 Run K-mean Cluster
```{r}
csna <- read.csv("CSNA_MLT.csv", sep = ",", header = TRUE)
x <- csna[,4:17] # select 14 binary vairables
WSSvector <- c(0,0,0,0,0,0,0,0,0)
for (i in 1:9)
{ cl <- kmeans(x, i)
WSSvector[i] <- cl$tot.withinss
} # partition the data set into 1-9 clusters and record total within SS for each solution
plot(WSSvector,type="l",xlab="# clusters",ylab="total SSW") # plot the total within-cluster sum of squares against the number of clusters
```

I use default cluster seeds, i.e. random seeds -- randomly select a set of n points as a first guess of the means of the clusters.

There seems to be no anomalies in the plot. The total SSW decreases gradually from 1 to 9 clusters indicating the increase of the accuracy of clustering when the number of clusters goes higher.

## Step 2
The line plot above shows evidence for 5-9 clusters. I will choose 6 as the optimal number of clusters.
```{r}
cl6 <- kmeans(x, 6) # re-run the optimal solution
csna$cl6 <- cl6$cluster # save the cluster membership of each case as a new varibale in the data frame csna
csna$cl6
```

## Step 3
```{r}
cl6$centers # means of the 14 variables by cluster
(cl6$withinss)^0.5 # standard deviations of the 14 variables by cluster
library(descr)
crosstab(csna$spec, csna$cl6) # do a CROSSTABS of the obtained cluster memberships with the "academic specialty or discipline" variable ("spec")
```

## Step 4
From the crosstable above, there are 32 *spec*s of psychology, 24 *spec*s of statistics, and 10 *spec*s of business applications in Cluster 1, which suggests most members in this cluster are likely to be marketing personnel.

There are 16 *spec*s of statistics, 12 *spec*s of computer science, 10 *spec*s of biology, and 10 *spec*s of math in Cluster 2, which suggests most members in this cluster are likely to be biological engineers.

There are 20 *spec*s of statistics, 12 *spec*s of psychology, and 12 *spec*s of biology in Cluster 3, which suggests most members in this cluster are likely to be psychological counsellors.

There are 20 *spec*s of computer science, 18 *spec*s of statistics, 10 *spec*s of psychology, and 10 *spec*s of biology in Cluster 4, which suggests most members in this cluster are likely to be experimental psychologists.

There are 1 *spec*s out of 4 of agriculture, 1 *spec*s out of 3
 of anthropology and 2 *spec*s out of 2 of geography in Cluster 5, which suggests members in this cluster are likely to work for the government.
 
There are 5 *spec*s of computer science, 4 *spec*s of biology, 4 *spec*s of math, and 4 *spec*s of psychology in Cluster 6, which suggests most members in this cluster may be students in biological psychology programs.